Cooperative Kernels: Safe Multitasking for Blocking Algorithms on GPUs

### 2016-11-13 write-ups/PLDI/paper.tex
First try on sizing non-persistent tasks

\subsection{Determining Representative Workloads}\label{sec:representativeworkloads}

\ADComment{Better section title?}
\HEComment{Dimensioning Non-persistent Workloads}

To assess how cooperative blocking algorithms can be, we fire lightweight
but still meaningful workloads that requires workgroups to be taken from
the blocking algorithms.

We tried to measure how much GPU computation is required to maintain
smooth animation on the screen during typical desktop usage. We model
these transient \HEComment{no sure about meaning if transient here}
using

The idea is
to run an infinite loop that launches a given kernel

\ADComment{Hugues, can you please explain your experimental
  methodology for working out required response times here?}

>>>>

\subsection{Sizing Non-Persistent Workloads}\label{sec:representativeworkloads}

\HEComment{given the paper title, maybe ``non-blocking'' would be more
  appropriate than ``non-persistent''?}

Cooperative kernels enables other \emph{non-persistent} workloads to
access GPU resources without stopping the blocking algorithm
computation entirely. We size these workloads to represent
approximatively the workload required by a system to maintain smooth
screen animations. We repetitively ran a kernel with a controlled
workload and detected from which workload size the screen animation
started to jitter. Given the kernel workload and its scheduling
frequency, we can infer what is the workload and frequency needed by
the system to maintain a smooth animation.

Based on this approach, we measured workloads required by the system
to maintain smooth animations of three types: (\emph{light}) emphasis
of desktop icons under the mouse pointer, (\emph{medium}) window
dragging over the desktop, and (\emph{heavy}) WebGL animations in a
browser. \mytab~\ref{tab:nonpersistentworkload} illustrates our
results. In order to simulate such non-persistent workloads alongside
kernels of blocking algorithms, we use a matrix multiplication kernel
where matrix dimensions are tuned to trigger the relevant execution
duration.

\begin{table}
\small
\centering
\begin{tabular}{ l c c }
workload & duration (ms) & period (ms)\\
\hline
light & 3 & 70\\
medium & 3 & 40\\
heavy & 10 & 40\\
\end{tabular}
\caption{Caracteristics of non-persitent workloads}
\label{tab:nonpersistentworkload}
\end{table}
